Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-23 analysis/paper/paper.Rmd

The Lincoln-Petersen estimator can be biased with small samples, so we also investigated the Chapman-modified Lincoln-Petersen estimator which is shown below.
$$
\hat{N} = \frac{(M + 1)(n + 1)}{(m + 1)} - 1
$$
The Schnabel estimator is shown below, where the $M$, $n$ and $m$ are indexed by the sampling occasion, $i$. In our example, the sampling occasions are defined as each day of sampling. This estimator does not have an associate standard error, but 95% confidence intervals can be calculated.
$$
\hat{N} = \frac{\sum\limits_{i = 1}^k n_i M_i}{\left(\sum\limits_{i = 1}^k m_i \right) + 1}
$$
There is another estimator for this type of multiple census surveys, called the Schumacher-Eschmeyer estimator, which is based on minimizing the weighted sum of squares between the proportion of marked individuals in the sample and the unknown proportion of marked individuals in the population. It is shown below.

>>>>

The Lincoln-Petersen estimator can be biased with small samples, so we also investigated the Chapman-modified Lincoln-Petersen estimator which is shown below.

$$
\hat{N} = \frac{(M + 1)(n + 1)}{(m + 1)} - 1
$$

The Schnabel estimator is shown below, where the $M$, $n$ and $m$ are indexed by the sampling occasion, $i$. In our example, the sampling occasions are defined as each day of sampling. This estimator does not have an associate standard error, but 95% confidence intervals can be calculated. The Schnabel estimator is essentially a weighted average of a series of Lincoln-Petersen estimators (with a Chapman modification).

$$
\hat{N} = \frac{\sum\limits_{i = 1}^k n_i M_i}{\left(\sum\limits_{i = 1}^k m_i \right) + 1}
$$

There is another estimator for this type of multiple census surveys, called the Schumacher-Eschmeyer estimator, which is based on minimizing the weighted sum of squares between the proportion of marked individuals in the sample and the unknown proportion of marked individuals in the population. It is shown below.
